---
title: "Basic_Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The following sports are supported by `collegeballR`

```{r,message=FALSE,warning=FALSE,echo=FALSE}
library(dplyr)
library(huxtable)
library(collegeballR)
table <- huxtable(sport_df,add_colnames = T) %>% 
  theme_article %>% 
  set_top_border(1, 1, 1) 
caption(table) <- "Table 1. Sports supported by collegeballR"
table
```

### Team Mappings

The team mapping function helps identify the team_id associated with specific teams for different sports. This is vital to know when using `player_stats` or `team_stats`.

```{r,message=FALSE,warning=FALSE}
teams <- team_mapping(2016,"Men's Basketball")
head(teams,6)
```

### Team Stats

Let's look at a quick example for the Texas A&M Women's Soccer team. 

```{r}
tamu_ws <- team_stats(697, 2015, "Women's Soccer",by="Season")
table2 <- huxtable(tamu_ws,add_colnames = T) %>% 
  theme_article %>% 
  set_top_border(1,1,1)
caption(table2) <- "Table 2. TAMU Women's Soccer 2015"
wrap(table2) <- TRUE
table2
```

### Player Stats

Here is a simple example of how to extract player stats, you can navigate to the other vignette for a more advanced example using purrr. 


```{r}
tamu_p_mbb <- player_stats(697, 2015, "MBB",by="Season")
table3 <- huxtable(tamu_p_mbb,add_colnames = T) %>% 
  theme_article %>% 
  set_top_border(1,1,1)
caption(table3) <- "Table 3. TAMU Men's Basketball 2015 - Player Stats"
wrap(table3) <- TRUE
table3
```

```

